\newpage

\section{Introduction}

Unraveling causal relations is a fundamental object of interest in science.
Causality testing is an important branch of time series analysis.
Granger \cite{granger69} stated a flexible theoretical problem definition for causality in his seminal paper in 1969.
His method laid ground for abundance of causality test implementations among many fields:
physics, economics, neuroscience, climate studies and other. 

Spectral methods of time series analysis enable investigatation of its features in different frequency domains.
Wavelet approach allows to transform signals without loosing spatial information, overcoming technical limitations of Fourier analysis.
One more sentence about how superior wavelet approach is.

In this thesis a non-linear Granger test is employed to investigate causal relations in multiple time scales between X and Y.
Section \ref{motivation} contains literature review and motivation for research,
section \ref{methodology} decribes in detail methodology used for data analysis.
Data sets used in this research are described in section \ref{data},
section \ref{results} gathers important results and gives insights about discovered causal relationships.
Lastly, closing remarks are presented in section \ref{conclusion}.

\section{Motivation} \label{motivation}

\section{Methodology} \label{methodology}
	\subsection{Granger causality}
Very important section about Granger causality \cite{granger69}.
		\subsubsection{Diks-Panchenko method}

	\subsection{Wavelet decomposition}
		\subsubsection{Daubechies wavelet}

\section{Dataset} \label{data}

\section{Results} \label{results}

\section{Conclusion} \label{conclusion}
